---
title: "csv_to_igraph"
author: '29189'
date: "2024-05-23"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Pipeline so far:
1) combine_folder_multiprocess.py --> python3 combine_folder_multiprocess.py reddit/comments --value amcstock
* change the above so that the file location of reddit/comments is accurate, run on the entire folder with the zst files

2) own_to_csv.py to convert to csv

3) combine output files using combine_csv.py


```{r}
# Load required libraries
library(tidyverse)
library(digest)
```
 
1) Load the data
```{r}
# Load the data
raw_data_comments <- read.csv("C:\\Users\\rhrou\\OneDrive - London School of Economics\\Dissertation Data\\02-2021-12-2021_combined_csv\\full_comments_2021.csv")

raw_data_submissions <- read.csv("C:\\Users\\rhrou\\OneDrive - London School of Economics\\Dissertation Data\\02-2021-12-2021_combined_csv\\full_submissions_2021.csv")
```

2) Data processing and username anonymization
```{r}
# Remove deleted comments and submissions, ie. those with no user information
comments <- raw_data_comments %>%
  filter(author != "[deleted]")
submissions <- raw_data_submissions %>%
  filter(author != "[deleted]")

# Anonymize the usernames using a hash function
hash_username <- function(username) {
  return(digest(username, algo = "sha256"))
}
comments$author <- sapply(comments$author, hash_username)
submissions$author <- sapply(submissions$author, hash_username)

# Filter out submissions that were removed by reddit, mods, users, etc.
submissions <- submissions %>% 
  filter(grepl("moderator", removed_by_category) == FALSE) %>% 
  filter(grepl("deleted", removed_by_category) == FALSE) %>%
  filter(grepl("author", removed_by_category) == FALSE) %>%
  filter(grepl("automod_filtered", removed_by_category) == FALSE) %>%
  filter(grepl("reddit", removed_by_category) == FALSE) %>%
  filter(grepl("copyright_takedown", removed_by_category) == FALSE)

# Variable selection for comments
comments <- comments %>% 
  select(author, created_utc, link_id, score, parent_id, id, gilded, stickied, body, is_submitter, permalink, name, stickied)

# Variable selection for submissions
submissions <- submissions %>% 
  select(author, created_utc, id, is_meta, is_original_content, is_reddit_media_domain, score, title, selftext, num_comments, gilded, stickied, permalink, upvote_ratio, can_mod_post, link_flair_text, title, media, media_embed, subreddit_subscribers, title, url, view_count)

# Save the processed data
save(comments, submissions, file = "processed_data.RData")

# Note that some comments may be linked to deleted submissions which are not saved, nonetheless sub comment interactions within these deleted submissions are still used in network interactions
```